\documentclass{article}

\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[margin = 0.5in, top=0.35in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{marvosym}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}

%%%%%%%%%%%%%%%
% DEFINITIONS %
%%%%%%%%%%%%%%%

\definecolor{MyBlue1}{RGB}{28, 43, 112}
\definecolor{MyBlue2}{RGB}{35, 54, 140}
\definecolor{MyBlue3}{RGB}{42, 65, 168}

\newcommand{\smallbullet}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ }

\pagestyle{empty}
\setlength\columnsep{30pt}

\titleformat{\section}{\color{MyBlue2}\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\color{MyBlue1}\bfseries\large}{}{0em}{}
\titleformat{\subsubsection}[runin]{\bfseries}{}{0em}{}[:]

\titlespacing{\section}{0em}{0em}{0em}
\titlespacing{\subsection}{0em}{0em}{0.25em}
\titlespacing{\subsubsection}{0em}{0em}{0.25em}

\setlength{\leftmargini}{16pt}
\setlength{\parindent}{0pt}

\setlist{nolistsep}

\renewcommand{\maketitle}{
    \begin{center}
    {\color{MyBlue3}\Huge\bfseries
        \theauthor
    }

    \vspace{0.1em}
    {
        \href{mailto:a8kumar@uwaterloo.ca}{\faEnvelope \ a8kumar@uwaterloo.ca} \quad
        \href{https://github.com/arnavcs}{\faGithub \ arnavcs} \quad
        \href{https://arnavcs.github.io/}{\faGlobe \ arnavcs.github.io} \quad
        \href{https://www.linkedin.com/in/arnav-kumar-0644881a3/}{\faLinkedin \ Arnav Kumar}
    }
    \vspace{-1em}
    \end{center}
}

\newenvironment{resumeItem}
{
    \vspace{0.5em}
}
{
}

\newcommand{\projectHead}[3]{
    \textbf{#1} $\vert$ \textit{#2} \\[-1.2em]
}

\newcommand{\achievement}[3]{
    #1, \textbf{#2} \dotfill #3 \\[-1.2em]
}

\newcommand{\experienceHead}[4]{
    \textbf{#1} @ #2 \hfill #3 \\[-1.2em]
}

\newenvironment{resumeList}
{
    \begin{itemize}[label=\smallbullet]
}
{
    \end{itemize}
}

%%%%%%%%%%%
% CONTENT %
%%%%%%%%%%%

\begin{document}

\title{R\'esum\'e}
\author{Arnav Kumar}

\maketitle

%% EXPERIENCE

\section{Experience}

\begin{resumeItem}
\experienceHead{Blockchain Software Engineer}{Dandelion Networks}{May 2023 - Aug 2023}{Online}
\begin{resumeList}
    \item Developed and implemented an enhanced lattice syncing and node discovery algorithm in Go, querying peers with Protocol Buffers to identify and address missing blocks in the local lattice with secure and concurrent updates.
    \item Created and deployed a locally hosted debugging website in Go to be run by each node of the blockchain network.
    \item Designed multiple mock servers, clients, and services to create multiple tests for the syncing and discovery algorithms with Go's Ginkgo and Gomega testing frameworks.
    \item Integrated Jenkins with the project through a Jenkinsfile to automatically build, test, vet, and format pushed code.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\experienceHead{Data Science Intern}{Tektorch.ai}{Apr 2022 - Aug 2022}{Online}
\begin{resumeList}
    \item Extracted features such as job title, location, classification, and pay from a job listing website using Python, Beautiful Soup 4, NumPy, and Pandas to create a dataset for analysis. 
    \item Developed an end-to-end data visualization pipeline to ingest data and display trends using Matplotlib, and NumPy.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \experienceHead{Math Competition Teacher}{Webber Academy}{Aug 2021 - June 2022}{Calgary, AB.}
% \begin{resumeList}
%     \item Taught 4 children competition mathematics every week for 90 minutes after school.
% \end{resumeList}
% \end{resumeItem}

\begin{resumeItem}
\experienceHead{Machine Learning Research Intern}{University of Alberta}{Jul 2021 - Aug 2021}{Online}
\begin{resumeList}
    \item Trained and employed natural language processing models to help determine the cause of a change in depressive language in Tweets as part of a psychology study.
    \item Created an evaluation framework with graphs and videos to analyse subject mouse position data during exams.
    \item Developed automation pipeline in Bash to reduce time spent by $20\times$ on the application of the evaluation framework.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \experienceHead{Coding Instructor}{Code Ninjas West Springs}{Mar 2022 - Apr 2022}{Calgary, AB.}
% \begin{resumeList}
%     \item Taught over 45 students to complete programming challenges in Scratch, MakeCode, and JavaScript.
%     \item Managed the progress of the students and directly relayed feedback to the manager.
% \end{resumeList}
% \end{resumeItem}

%% PROJECTS

\section{Projects}

\begin{resumeItem}
\projectHead{\href{https://github.com/youssefsoli/IPFE}{InterPlanetary File Explorer (IPFE)}}{Go, Python, Scikit-learn, Estuary, Co:here, Three.js}{Jan 2023}
\begin{resumeList}
    \item Created vector embeddings for files with their headers using Co:here's NLP embeddings to facilitate classification of files.
    \item Performed principal component analysis of the vector embeddings to reduce the dimensionality from 4096 to 3 to be plotted and displayed interactively in 3D space using Three.js.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/OSIC-IPF}{Prognosing Idiopathic Pulmonary Fibrosis (IPF)}}{Python, Tensorflow2, Pandas, Scikit-learn}{Dec 2020 - Jun 2021}
\begin{resumeList}
    \item Implemented an auto-encoder, linear regression, dense neural network, and bayesian model in order to accurately predict future lung capacity and give a confidence value using initial lung capacity data, age, sex, smoking status, and more.
    \item Obtained a Laplace Log Likelihood score of $-6.9$ (much better than the baseline score $-8.1$) with $\sigma \approx 200$mL.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/quack-stack}{Custom Language Interpreter}}{Haskell}{May 2023 - Present}
\begin{resumeList}
    \item Created an expression evaluator for a self-made stack-based language.
    \item Implemented zipper traversal to determine which part of the stack has already been processed in a followable, stepwise manner.
\end{resumeList}
\end{resumeItem}

\begin{resumeItem}
\projectHead{\href{https://github.com/arnavcs/cli-chess}{CLI Chess}}{Haskell}{Aug 2022 - Present}
\begin{resumeList}
    \item Created a local mulitplayer clone of the game of chess in Haskell that can be played in the CLI with the Haskell REPL.
    \item Developed safe and scalable functions to determine the state of the board and indentify check and checkmate.
    \item Employed lists as applicative functors and monads to write concise, readable code for determining all valid next moves.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/flashcards}{CLI Flashcards}}{Bash}{Apr 2022 - Apr 2022}
% \begin{resumeList}
%     \item Built a command line tool to add terms to and practice with a flashcard set that the user can create.
%     \item Implemented several flag options, including a help option, version option, and script update option.
% \end{resumeList}
% \end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/ASCII-art}{Braille ASCII Art Generator}}{Python, OpenCV}{Apr 2021 - Jul 2021}
% \begin{resumeList}
%     \item Used thresholding in OpenCV to determine which pixels of the output art should be shaded.
%     \item Transformed the image array into braille characters using 3x2 pixel filters which returned a binary number corresponding to a braille character.
% \end{resumeList}
% \end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/arnavcs.github.io}{Modular Personal Website}}{JavaScript, HTML, CSS}{Mar 2022 - Aug 2022}
% \begin{resumeList}
%     \item Built a simple content management system (CMS) with JavaScript to generate a DOM object from given data.
%     \item Added JSON based templating to easily modify website based on the type of information being conveyed.
% \end{resumeList}
% \end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/black-jack}{Blackjack}}{C++}{Apr 2021 - Jul 2021}
% \begin{resumeList}
%     \item Used object oriented programming to implement a local multiplayer blackjack game with a computer playing as the house.
%     \item Probabilistically optimized the holding value that the computer house uses.
% \end{resumeList}
% \end{resumeItem}

% \begin{resumeItem}
% \projectHead{\href{https://github.com/arnavcs/game-of-life}{Conway's Game of Life}}{Javascript}{Apr 2020 - Mar 2020}
% \begin{resumeList}
%     \item Created a javascript web version of Conway's Game of Life where a user-chosen number of generations can be simulated.
%     \item Enabled the user to choose an initial arrangement of live and dead cells as well as the size of the initial grid.
% \end{resumeList}
% \end{resumeItem}
    
%% ACHIEVEMENTS

\section{Achievements}

\begin{resumeItem}
\begin{resumeList}
    \item \achievement{$335^{\mathrm{th}}$ (top $10\%$), with score $26$}{William Lowell Putnam Mathematical Competition}{2022}
    \item \achievement{Estuary Sponsor Prize Winner}{UofTHacks X}{2023}
    \item \achievement{$10^{\mathrm{th}}$ in Canada}{Asian Pacific Mathematics Olympiad}{2022}
    \item \achievement{$11^{\mathrm{th}}$ in Canada}{Canadian Association of Physicists High School Exam}{2022}
    % \item \achievement{$12^{\mathrm{th}}$ in Canada, $17^{\mathrm{th}}$ internationally}{Sir Isaac Newton Physics Exam}{2021 - 2022}
    \item \achievement{$18^{\mathrm{th}}$ in Canada, 2 time qualifier}{Canadian Mathematical Olympiad}{2021 - 2022}
    % \item \achievement{Canadian Honour Roll, Top in Alberta}{Canadian Open Mathematics Challenge}{2017 - 2022} % Gold or Silver Alberta medalist every year
    % \item \achievement{2 time qualifier}{American Invitational Mathematics Exmaination}{2021 - 2022}
    % \item \achievement{Part II winner, 3 time part I winner}{Alberta High School Mathematics Competition}{2018 - 2022} % perfect score in part I, AHSMC fellow
    \item \achievement{Invited to write}{United States of America Mathematical Olympiad}{2022}
    \item \achievement{Bronze medalist for machine learning project on prognosing IPF}{Canada Wide Science Fair}{2021}
\end{resumeList}
\end{resumeItem}

%% EDUCATION

\section{Education}

\begin{resumeItem}
\experienceHead{Candidate for BSc. Computer Science}{University of Waterloo}{2022 - Present}{Waterloo, ON.}
\begin{resumeList}
    \item Received the Ronald G. Dunkley National Scholarship (\$18,000), the President's Entrance Scholarship (\$2,500), and the Cenovus Energy STEM Scholarship (\$14,000).
    \item Core average of 98\% (4.0 GPA) with all advanced level courses and received term distinction.
\end{resumeList}
\end{resumeItem}

% \begin{resumeItem}
% \experienceHead{International Summer School for Young Physicists (ISSYP)}{Perimeter Institute for Theoretical Physics}{Summer 2021}{Online}
% \end{resumeItem}

% \begin{resumeItem}
% \experienceHead{Quantum Cryptography School for Young Students (QCSYS)}{Institute for Quantum Computing, University of Waterloo}{Summer 2020}{Online}
% \end{resumeItem}

% \begin{resumeItem}
% \experienceHead{High School Diploma}{Webber Academy}{2008 - 2022}{Calgary, AB.}
% \begin{resumeList}
%     \item President of the Student Union and annual merit scholarship recipient.
% \end{resumeList}
% \end{resumeItem}

%% SKILLS 

\section{Skills}

\begin{resumeItem}
\subsubsection{Languages}
Go, Python, C++, JavaScript, Haskell, Racket, Java, Bash, {\LaTeX}, HTML, CSS, Markdown, RegEx

\subsubsection{Frameworks}
Linux, Unix, Protobuf, Gomega, Ginkgo, Pandas, Matplotlib, NumPy, Beautiful Soup, Tensorflow, Scikit-learn, OpenCV
\end{resumeItem}

\end{document}
